Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-16 supp/supp.qmd
change to html as it's cleaner looking and better res figs

---
title: "Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
  pdf:
    include-in-header: 
      text: '\usepackage{lineno}\linenumbers'
  html:
    highlight: pygments
    theme: solarized-light
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

>>>>

---
title: "Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  html:
    highlight: pygments
    theme: solarized-light
  docx:
    reference-doc: ../bib/template.docx
  pdf:
    include-in-header: 
      text: '\usepackage{lineno}\linenumbers'
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---
